### 2020-01-27 model.tex
Edit chp 3 and equations

The group constants relevant for neutronics calculations in Moltres are the
macroscopic fission, absorption, and scattering neutron cross sections,
neutron diffusion coefficients, average fission energies, average neutron
yields, inverse neutron speeds, flux spectra, \gls{DNP} decay constants, and
effective delayed neutron fractions. These group constants are extracted from
the Serpent output files using a Python script available from the Github
repository that holds the Moltres source code. The script rewrites the group
constants into a format that Moltres can read.

@@

Focussing our attention on Moltres, the neutronics calculations are
implemented through the standard formulation of the time-dependent multi-group
neutron diffusion equations and \gls{DNP} concentration equations as shown in
equations * and *:
%
\begin{align}
	\frac{1}{v_g} \frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla
	\phi_g + \Sigma^r_g \phi_g
	= \sum^G_{g \neq g'} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
	\sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
	\lambda_i C_i, \label{eq1}
\end{align}
%
\begin{align}
	\frac{\partial C_i}{\partial t} = \sum^G_{g'=1} \beta_i \nu \Sigma^f_{g'}
	\phi_{g'} - \lambda_i C_i - \nabla \cdot u C_i. \label{eq2}
\end{align}
%
where
{\small
%
\begin{align*}
	v_g &= \text{average speed of neutrons in group }g \\
	\phi_g &= \text{flux of neutrons in group }g \\
	t &= \text{time} \\
	D_g &= \text{diffusion coefficient of neutrons in group }g \\
	\Sigma^r_g &= \text{macroscopic cross-section for removal of neutrons from
	group }g \\
	\Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross-section of
	scattering from }g' \text{ to }g \\
	\chi^p_g &= \text{prompt fission spectrum neutrons in group }g \\
	G &= \text{total number of discrete neutron groups} \\
	\nu &= \text{average number of neutrons produced per fission} \\
	\Sigma^f_{g} &= \text{macroscopic fission cross-section for neutron in group }g \\
	\chi^d_g &= \text{delayed fission spectrum neutrons in group }g \\
	I &= \text{total number of delayed neutron precursor groups} \\
	\beta &= \text{total delayed neutron fraction} \\
	\beta_i &= \text{delayed neutron fraction of precursor group i} \\
	\lambda_i &= \text{average decay constant of delayed neutron precursors in precursor group }i \\
	C_i &= \text{concentration of delayed neutron precursors in precursor group }i
\end{align*}
}
%

Moltres users may call for an arbitrary number of neutron energy groups as
long as they provide Moltres with the appropriate group constant data. The
number of precursor groups is also arbitrary, though usually pre-determined by
the choice of nuclear data library in the group constant generation step.
Moltres automatically interpolates the group constant data for required
temperatures using one of the many pre-defined interpolation methods available
in \gls{MOOSE}. Once again, users have the freedom to select their
interpolation method of choice.

@@

The governing equation for temperature in the molten salt is given as:
%
\begin{align}
	\rho c_{p} \frac{\partial T}{\partial t} + \nabla \cdot \big( \rho
	c_{p} \overrightarrow{u} \cdot T - k \nabla T \big) = Q_s - Q_{hx},
	\label{eq3}
\end{align}
%
	where
{\small
\begin{align*}
	\rho &= \text{density of molten salt} \\
	c_{p} &= \text{specific heat capacity of molten salt} \\
	T &= \text{temperature of molten salt} \\
	\overrightarrow{u} &= \text{velocity of molten salt} \\
	k &= \text{thermal conductivity of molten salt} \\
	Q_{hx} &= \text{heat sink},
\end{align*}
}
	and the source term $Q_s$ is given as:
%
\begin{align}
Q_s = \sum^G_{g=1} \epsilon_g \Sigma_g^f \phi_g. \label{eq4}
\end{align}

>>>>

The group constants relevant for neutronics calculations in Moltres are the
macroscopic fission, absorption, and scattering neutron cross sections,
neutron diffusion coefficients, average fission energies, average neutron
yields, inverse neutron speeds, flux spectra, \gls{DNP} decay constants, and
effective delayed neutron fractions. These group constants are extracted from
the Serpent output files using a Python script available from the Github
repository that holds the Moltres source code. The script rewrites the group
constants into a Moltres-compatible format.

@@

Focusing our attention on Moltres, the neutron flux calculations are
performed using the standard formulations for the time-dependent multi-group
neutron diffusion equations and \gls{DNP} concentration equations as shown in
equations \ref{eq:neut} and \ref{eq:dnp}:
%
\begin{align}
	\frac{1}{v_g} \frac{\partial \phi_g}{\partial t} &= \nabla \cdot D_g
	\nabla \phi_g - \Sigma^r_g \phi_g
	\sum^G_{g \neq g'} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
	\sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
	\lambda_i C_i, \label{eq:neut} \\
	\frac{\partial C_i}{\partial t} &= \beta_i \sum^G_{g'=1} \nu \Sigma^f_{g'}
	\phi_{g'} - \lambda_i C_i - \boldsymbol{u} \cdot \nabla C_i + \nabla \cdot
	\frac{\mu_t}{\rho Sc_t} \nabla C_i, \label{eq:dnp} \\
	\intertext{where} v_g &= \text{average speed of neutrons in group }g 
	\nonumber \\
	\phi_g &= \text{flux of neutrons in group }g \nonumber \\
	t &= \text{time} \nonumber \\
	D_g &= \text{diffusion coefficient of neutrons in group }g \nonumber \\
	\Sigma^r_g &= \text{macroscopic cross-section for removal of neutrons from
	group }g \nonumber \\
	\Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross-section of
	scattering from }g' \text{ to }g \nonumber \\
	\chi^p_g &= \text{prompt fission spectrum neutrons in group }g \nonumber
	\\
	G &= \text{total number of discrete neutron groups} \nonumber \\
	\nu &= \text{average number of neutrons produced per fission} \nonumber \\
	\Sigma^f_{g} &= \text{macroscopic fission cross-section for neutron in
	group }g \nonumber \\
	\chi^d_g &= \text{delayed fission spectrum neutrons in group }g \nonumber
	\\
	I &= \text{total number of delayed neutron precursor groups} \nonumber \\
	\beta &= \text{total delayed neutron fraction} \nonumber \\
	\beta_i &= \text{delayed neutron fraction of precursor group i} \nonumber
	\\
	\lambda_i &= \text{average decay constant of delayed neutron precursors in
	precursor group }i \nonumber \\
	C_i &= \text{concentration of delayed neutron precursors in precursor
	group }i \nonumber
\end{align}
%

The limitations of the multi-group neutron diffusion compared to
S$_{\text{N}}$ and Monte Carlo methods are well-documented but they provide
decent accuracy at lower computational costs. A comparison of the
multiplication factor and reactivity coefficients in the context of the
\gls{MSFR} is provided in the results section.

The \gls{DNP} concentration equation has an additional advection term to
account for the movement of \glspl{DNP} in the primary coolant loop. Moltres
also accounts for the decay of \glspl{DNP} outside the active core
region by simulating its flow in a separate 1D geometry. The length and
velocity defined in this geometry may differ according to reactor
specifications.

Moltres users may call for an arbitrary number of neutron energy groups as
long as they provide Moltres with the appropriate group constant data. The
number of precursor groups is also arbitrary, though usually pre-determined by
the choice of nuclear data library in the group constant generation step.
Moltres automatically interpolates the group constant data for required
temperatures using one of the many pre-defined interpolation methods available
in \gls{MOOSE}. Once again, users have the freedom to select their
interpolation method of choice. For this work, we have selected six neutron
energy groups according to the energy boundaries in table *, eight \gls{DNP}
groups as defined by the JEFF-3.1.2 library, and the spline interpolation
method.

For the decay heat model, previous studies on the MSFR * have shown that
using three decay heat precursor groups with different half-lives can model
decay heat in the MSFR for up to 300 seconds after shutdown with a relative
error of less than 2 \%. Thus, we implemented the decay heat model using
equations similar to the \gls{DNP} equations, as shown in eq
\ref{eq:decayheat}:
%
\begin{align}
	\frac{\partial D^k}{\partial t} &= f_k \sum^G_{g'=1} \epsilon_{g'}
	\Sigma^f_{g'} \phi_{g'} - \lambda^k D^k - \boldsymbol{u} \cdot \nabla D^k
	+ \nabla \cdot \frac{\mu_t}{\rho Sc_t} \nabla D^k, \label{eq:decayheat} \\
	\intertext{where}
	D^k &= \text{concentration of decay heat precursors in group }k \nonumber
	\\
	f_k &= \text{fraction of decay heat to total power at steady state}
	\nonumber \\
	\epsilon_g &= \text{average fission energy} \nonumber \\
	\lambda^k &= \text{average decay constant of decay heat precursors in
	group }k. \nonumber
\end{align}

@@

The governing equation for temperature in the molten salt is given as:
%
\begin{align}
	\rho c_{p} \frac{\partial T}{\partial t} &= - \nabla \cdot \big( \rho
	c_{p} \overrightarrow{u} \cdot T - k \nabla T \big) + Q_s - Q_{hx},
	\label{eq3}
	\intertext{where}
	\rho &= \text{density of molten salt} \nonumber \\
	c_{p} &= \text{specific heat capacity of molten salt} \nonumber \\
	T &= \text{temperature of molten salt} \nonumber \\
	\overrightarrow{u} &= \text{velocity of molten salt} \nonumber \\
	k &= \text{thermal conductivity of molten salt} \nonumber \\
	Q_{hx} &= \text{heat sink},
\end{align}
	and the source term $Q_s$ is given as:
%
\begin{align}
Q_s = \sum^G_{g=1} \epsilon_g \Sigma_g^f \phi_g. \label{eq4}
\end{align}

In the \gls{MSFR}, salt flow in the core has a Reynolds number on the order of
10$^6$*. Thus the Navier-Stokes module in \gls{MOOSE} cannot sufficiently
capture the turbulent flow behavior. Furthermore, the \gls{MSFR} benchmark
geometry encourages the formation of turbulent recirculation regions in the
fuel salt near the blanket tank regions. Due to this present limitation, only
the flow in the active core region is simulated and it is assumed to be
vertical flow. This eliminates the presence of recirculation zones reported by
*, which will likely be a source of discrepancy between our results and
theirs. Another consequence is the absence of turbulent diffusion, resulting
in higher-than-expected temperatures along the central axis of the reactor
where the neutron flux and heat generation is highest. This is further
exacebated by the high Prandtl number of the molten salt; heat transfer is
dominated by convective flow. This means that there would be very low heat
transfer observed by diffusion due to the negligible contributions from
heat conduction.

### 2020-01-27 msr.tex
Edit chp 3 and equations

>>>>

\section{Molten Salt Fast Reactor}

The \gls{MSFR} is a reference fast-spectrum \gls{MSR} concept developed
under the \gls{EVOL} project. Inspired by the \gls{MSBR}, the \gls{MSFR} is
intended to run primarily on a closed thorium fuel cycle with
continuous online fuel reprocessing. Several reasons motivated the omission of
graphite moderators from the \gls{MSFR} design. Graphite is susceptible to
long-term radiation damage and replacement is likely to be necessary during
the operating lifetime of the reactor. The fast neutron spectrum improves
breeding ratios due to higher fission neutron yield in $^{233}$U and lower
parasitic absorption in non-fuel materials. Lastly, graphite has a positive
temperature coefficient of reactivity; eliminating graphite from the design
ensures a greater safety margin.

Power output of the \gls{MSFR} is rated at 3000 MW$_{\text{th}}$ and 1500
MW$_{\text{e}}$. The high thermal efficiency is achieved
